Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-26 paper.tex
Fixed note on multiple engines in tight integrations.

\paragraph{Scalability} Adding a new engine instance requires a new
instance of the science gateway, which is in general not possible
(\texttt{S$_1$}=2)\answerednote{Tristan}{What-about load-balancing between web
  server instances?}{Marc-e}{Would that really be considered a
  real architectural feature or an IT hack?}.  Distributed engines are
not available by default (\texttt{S$_2$}=1). The scheduling of tasks
on the infrastructure is as complex as in any other architecture since
the workflow engine might implement any kind of scheduling policy
(\texttt{S$_3$}=0).

>>>>

\paragraph{Scalability} Adding a new engine instance requires a new
instance of the science gateway, which is in general not possible
(\texttt{S$_1$}=2). Specific IT setups such as load-balancing between
web server instances might be used to deal with this
issue. \closedanswerednote{Tristan}{What-about load-balancing between web
  server instances?}{Marc-e}{Would that really be considered a real
  architectural feature or an IT hack?}{Tristan}{I agree, we should
  keep IT setups out of the picture. Depending on the internals of the
  science gateway, such hacks may or may not be feasible. I added a
  sentence to mention this possibility, without changing the score.}
Distributed engines are not available by default
(\texttt{S$_2$}=1). The scheduling of tasks on the infrastructure is
as complex as in any other architecture since the workflow engine
might implement any kind of scheduling policy (\texttt{S$_3$}=0).
